---
title: "Function Network Graph"
description: >
  A force directed graph highlighting the links between functions
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function Network Graph}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Functions in RobinHood are organized into 3 basic groups:

  - **Core** functions are what users will interact with
  - **API** functions are the backend functions that interact with a RobinHood connection
  - **Utility** functions are used in the background for integrity checks and convenience

The following force directed graphs display **core** and **API** functions in order to show the dependencies across functions. This might be helpful if you are wanting to understand the overall organization of the package and understand how the **API** functions support the **core** functions.

For those curious how I made these plots I used the [ggnet2](https://briatte.github.io/ggnet/) package.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.height = 8, fig.width = 12, warnings = FALSE, message = FALSE, comment = NA)
```


```{r data, echo=FALSE}
install.packages(c("igraph", "GGally", "network", "sna", "intergraph"))

library(igraph)
library(GGally)
library(network)
library(sna)
library(intergraph)

nodes <- data.frame()
nodes <- rbind(nodes, data.frame(func = "api_accounts",              type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_accounts_crypto",       type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_ach",                   type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_contracts",             type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_currency_pairs",        type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_endpoints",             type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_fundamentals",          type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_historicals",           type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_historicals_crypto",    type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_historicals_options",   type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_instruments",           type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_instruments_options",   type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_login",                 type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_logout",                type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_marketdata",            type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_markets",               type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_orders",                type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_orders_crypto",         type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_orders_options",        type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_portfolios",            type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_portfolios_crypto",     type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_positions",             type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_positions_crypto",      type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_positions_options",     type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_quote",                 type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_quote_crypto",          type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_ratings",               type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_tag",                   type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_tickers",               type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_user",                  type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "api_watchlist",             type = "API",     category = ""))
nodes <- rbind(nodes, data.frame(func = "cancel_ach_transfer",       type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "cancel_order",              type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "cancel_order_crypto",       type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "cancel_order_options",      type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_accounts",              type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_ach",                   type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_contracts",             type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_fundamentals",          type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_historicals",           type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_historicals_crypto",    type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_historicals_options",   type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_market_hours",          type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_order_history",         type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_order_history_crypto",  type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_order_history_options", type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_order_status",          type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_order_status_crypto",   type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_order_status_options",  type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_portfolios",            type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_positions",             type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_positions_crypto",      type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_positions_options",     type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_quote",                 type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_quote_crypto",          type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_ratings",               type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_tag",                   type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_tickers",               type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "get_user",                  type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "logout",                    type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "place_ach_transfer",        type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "place_order",               type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "place_order_crypto",        type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "place_order_options",       type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "RobinHood",                 type = "Core",    category = ""))
nodes <- rbind(nodes, data.frame(func = "watchlist",                 type = "Core",    category = ""))

edges <- data.frame()
edges <- rbind(edges, data.frame(from = "api_accounts",              to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_accounts_crypto",       to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_ach",                   to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_contracts",             to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_currency_pairs",        to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_fundamentals",          to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_instruments",           to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_login",                 to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_logout",                to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_marketdata",            to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_orders_crypto",         to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_orders_options",        to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_orders",                to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_marketdata",            to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_portfolios_crypto",     to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_portfolios_crypto",     to = "api_accounts_crypto",     api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_positions_crypto",      to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_positions_options",     to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_positions",             to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_ratings",               to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_tag",                   to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_tickers",               to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "api_user",                  to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "cancel_ach_transfer",       to = "api_ach",                 api_action = "PUT"))
edges <- rbind(edges, data.frame(from = "cancel_order_crypto",       to = "api_orders_crypto",       api_action = "PUT"))
edges <- rbind(edges, data.frame(from = "cancel_order_options",      to = "api_orders_options",      api_action = "PUT"))
edges <- rbind(edges, data.frame(from = "cancel_order",              to = "api_orders",              api_action = "PUT"))
edges <- rbind(edges, data.frame(from = "get_accounts",              to = "api_accounts",            api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_ach",                   to = "api_ach",                 api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_contracts",             to = "api_contracts",           api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_contracts",             to = "api_marketdata",          api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_fundamentals",          to = "api_fundamentals",        api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_historicals",           to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "get_historicals",           to = "api_historicals",         api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_market_hours",          to = "api_markets",             api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_market_hours",          to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "get_order_history_crypto",  to = "api_orders_crypto",       api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_history_crypto",  to = "api_currency_pairs",      api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_history_options", to = "api_orders_options",      api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_history",         to = "api_orders",              api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_history",         to = "api_instruments",         api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_status_crypto",   to = "api_orders_crypto",       api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_status_options",  to = "api_orders",              api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_order_status",          to = "api_orders",              api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_portfolios",            to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "get_portfolios",            to = "api_portfolios",          api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions_crypto",      to = "api_positions_crypto",    api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions_options",     to = "api_positions_options",   api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions_options",     to = "api_instruments_options", api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions_options",     to = "api_marketdata",          api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions",             to = "api_positions",           api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions",             to = "api_instruments",         api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_positions",             to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "get_positions",             to = "api_quote",               api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_quote_crypto",          to = "api_currency_pairs",      api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_quote_crypto",          to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "get_quote_crypto",          to = "api_quote_crypto",        api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_quote",                 to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "get_quote",                 to = "api_quote",               api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_ratings",               to = "api_ratings",             api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_tag",                   to = "api_tag",                 api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_tag",                   to = "api_instruments",         api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_tickers",               to = "api_tickers",             api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_tickers",               to = "get_fundamentals",        api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_user",                  to = "api_user",                api_action = "GET"))
edges <- rbind(edges, data.frame(from = "logout",                    to = "api_logout",              api_action = "POST"))
edges <- rbind(edges, data.frame(from = "place_ach_transfer",        to = "api_ach",                 api_action = "POST"))
edges <- rbind(edges, data.frame(from = "place_order_crypto",        to = "api_currency_pairs",      api_action = "GET"))
edges <- rbind(edges, data.frame(from = "place_order_crypto",        to = "api_orders_crypto",       api_action = "POST"))
edges <- rbind(edges, data.frame(from = "place_order_options",       to = "api_orders_options",      api_action = "POST"))
edges <- rbind(edges, data.frame(from = "place_order",               to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "place_order",               to = "api_quote",               api_action = "GET"))
edges <- rbind(edges, data.frame(from = "place_order",               to = "api_orders",              api_action = "POST"))
edges <- rbind(edges, data.frame(from = "RobinHood",                 to = "api_login",               api_action = "POST"))
edges <- rbind(edges, data.frame(from = "RobinHood",                 to = "api_accounts",            api_action = "GET"))
edges <- rbind(edges, data.frame(from = "watchlist",                 to = "api_endpoints",           api_action = "None"))
edges <- rbind(edges, data.frame(from = "watchlist",                 to = "api_watchlist",           api_action = "GET"))
edges <- rbind(edges, data.frame(from = "watchlist",                 to = "api_fundamentals",        api_action = "Mixed"))
edges <- rbind(edges, data.frame(from = "api_orders_crypto",         to = "api_accounts_crypto",     api_action = "GET"))
edges <- rbind(edges, data.frame(from = "api_portfolios_crypto",     to = "api_accounts_crypto",     api_action = "GET"))
edges <- rbind(edges, data.frame(from = "api_ratings",               to = "api_instruments",         api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_historicals_crypto",    to = "api_historicals_crypto",  api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_historicals_crypto",    to = "api_currency_pairs",      api_action = "GET"))
edges <- rbind(edges, data.frame(from = "api_instruments_options",   to = "api_historicals_options", api_action = "GET"))
edges <- rbind(edges, data.frame(from = "get_historicals_options",   to = "api_historicals_options", api_action = "GET"))

```

## Simplified Network with Endpoints Connection Removed

```{r simplified_network}

edges2 = subset(edges, api_action != 'None')

g2 <- simplify(graph_from_data_frame(edges2, vertices = nodes))

set.seed(1)
ggnet2(g2, size = 0, color = "type", edge.lty = "dashed", layout.exp = .15) +
  geom_point(aes(x = x, y = y), color = "grey15", size = 7) +
  geom_text(aes(label = label, x = x, y = y, color = color), size = 3) +
  scale_color_brewer(type = "qual", palette = 4, guide = FALSE) +
  theme(panel.background = element_rect(fill = "grey15"))



```


## Full Network

```{r complete_network}

g <- simplify(graph_from_data_frame(edges, vertices = nodes))

set.seed(1)
ggnet2(g, size = 0, color = "type", edge.lty = "dashed", layout.exp = .15) +
  geom_point(aes(x = x, y = y), color = "grey15", size = 7) +
  geom_text(aes(label = label, x = x, y = y, color = color), size = 3) +
  scale_color_brewer(type = "qual", palette = 4, guide = FALSE) +
  theme(panel.background = element_rect(fill = "grey15"))


```
